---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  message = FALSE
)
# Redirect the example query to the local test response corpus
httptest::use_mock_api()
```

# promr

`promr` is a [PromQL] query client for the [Prometheus] time-series database.

[PromQL]: https://prometheus.io/docs/prometheus/latest/querying/basics/
[Prometheus]: https://prometheus.io/

## Installation

To install the development version using `devtools`:

``` r
devtools::install_github("domodwyer/promr")
```

## Example

```{r query, echo=c(-4, -6)}
library(promr)

# Define your PromQL query
# nolint start: line_length_linter
q <- "sum by (handler, result) (rate(dml_handler_write_duration_seconds_count{}[1m]))"
# nolint end

# And execute the query within the specified time range
df <- query_range(
  q,
  "2022-08-19T00:00:00Z",
  "2022-08-20T00:00:00Z"
)
```

Timestamps can be provided as `rfc3339` strings, numerical unix timestamps, or
`POSIXct` objects. Optionally `timeout`, and `step`  parameters can be provided.

The output `df` contains all the returned series, with the measurements nested
within. For this query, there are 10 series:

```{r summary}
print(df)
```

The unnested data can be easily extracted using `tidyr::unnest()` (part of of
the `tidyverse`), to produce a “long” tibble of measurements:

```{r unnest}
df |>
  tidyr::unnest(values) |>
  head()
```

Which makes it easy to work on, and visualise the actual data:

```{r plot}
library(ggplot2)
library(tidyverse)

df |>
  unnest(values) |>
  filter(handler == "partitioner") |>
  ggplot(aes(x = timestamp, y = value, colour = result)) +
  geom_line() +
  labs(
    title = "Partitioner Calls",
    x = "Time",
    y = "Requests per Second"
  )
```
